---
title: 'Tidy Tuesday: College Major and Income'
author: "Vicente Guerrero"
date: "3/28/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Library Packages to load: 
```{r}
library(tidyverse)
library(scales)
theme_set(theme_light())
```

Reading and processing the data from tidyverse github
```{r}
recent_grads <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-16/recent-grads.csv")

majors_processed <- recent_grads %>% 
      arrange(desc(Median)) %>% 
      mutate(Major = str_to_title(Major), 
            Major = fct_reorder(Major, Median)) 
```

Adding gender totals to data
```{r by_major_category}
by_major_category <- majors_processed %>% 
   filter(!is.na(Total)) %>% 
   group_by(Major_category) %>% 
   summarize(Men = sum(Men), 
             Women = sum(Women),
             Total = sum(Total), 
             MedianSalary = sum(Median * Sample_size) / sum(Sample_size)) %>% 
   mutate(ShareWomen = Women/Total) %>% 
   arrange(desc(ShareWomen))
```

# Major Categories by Total Graduates
```{r}
by_major_category %>% 
   mutate(Major_category = fct_reorder(Major_category, Total)) %>% 
   gather(Gender, Number, Men, Women) %>% 
   ggplot(aes(Major_category, Number, fill = Gender)) +
   geom_col() + 
   coord_flip() + 
   scale_y_continuous(labels = comma_format()) + 
   labs(x = "",
        y = "Total Graduates", 
        title = "What are the Most Common Major Categories")
```

# Gender Breakdown for 20 Most Popular Majors
```{r}
majors_processed %>% 
   arrange(desc(Total)) %>% 
   head(20) %>% 
   mutate(Major = fct_reorder(Major, Total)) %>% 
   gather(Gender, Number, Men, Women) %>% 
   ggplot(aes(Major, Number, fill = Gender)) + 
   geom_col() + 
   coord_flip() + 
   labs( y = "Total Graduates") + 
   scale_y_continuous(labels = comma_format())
```

# What is the Median Salary Distribution for Each Major Category?
```{r}
majors_processed %>% 
      mutate(Major_category = fct_reorder(Major_category, Median)) %>% 
      ggplot(aes(x = Major_category, y = Median, fill = Major_category)) + 
      geom_boxplot() + 
      scale_y_continuous(labels = dollar_format()) + 
      coord_flip() + 
      expand_limits(y = 0) + 
      labs(x = "", 
           y = "Median Salary", 
           title = "Median Salary by Major Category") + 
      theme(legend.position = "none")
```

# Majors with the Highest Salaries:
```{r}
majors_processed %>% 
      filter(Sample_size >= 100) %>% 
      head(20) %>% 
      ggplot(aes(Major, Median, color = Major_category)) + 
      geom_point() + 
      geom_errorbar(aes(ymin = P25th, ymax = P75th)) + 
      expand_limits(y = 0) +
      scale_y_continuous(labels = dollar_format()) + 
      coord_flip() + 
      labs(title = "What Are the Highest-Earning Majors", 
           subtitle = "Top 20 Majors With At Least 100 Graduates Surveys. Bars Represent 25th and 75th Percentile",
           y = "Median Salary of Graduates", 
           x = "") + 
      theme(legend.position = "bottom") + 
      scale_color_discrete(name = "Major Category:")
```

# Majors with Lowest Unemployment Rate
```{r}
employment_rate <- majors_processed %>% 
   filter(Sample_size >= 100) %>% 
   arrange(Unemployment_rate) 

employment_rate %>% 
   head(10) %>% 
   mutate(Major = fct_reorder(Major, Unemployment_rate)) %>% 
   ggplot(aes(Major, Unemployment_rate, color = Major_category)) + 
   geom_point() + 
   expand_limits(y = 0) + 
   scale_y_continuous(labels = percent_format()) + 
   coord_flip() + 
   labs(y = "Unemployment Rate", 
        x = "") + 
   theme(legend.position = "bottom") + 
   scale_color_discrete(name = "Major Category")
```

# Linear Model for Median Salary and % of Women by Major
```{r}
library(plotly)

g <- majors_processed %>% 
   mutate(Major_category = fct_lump(Major_category, 4)) %>% 
   ggplot(aes(ShareWomen, Median, color = Major_category, size = Sample_size,
              label = Major)) + 
   geom_point() + 
   geom_smooth(aes(group = 1), method = "lm") + 
   expand_limits(y = 0) + 
   scale_y_continuous(labels = dollar_format()) + 
   scale_x_continuous(labels = percent_format()) + 
   labs(x = "Share of Women", 
        y = "Median Salary")

ggplotly(g)
```

```{r}
majors_processed %>% 
   select(Major, Total, ShareWomen, Sample_size, Median) %>% 
   #weighted linear regression, looking at Sample Size
   lm(Median ~ ShareWomen, data = ., weights = Sample_size) %>% 
   summary()
```
% of Women Est. SD of -23650 with P-Value = 2.2 * 10^-16. 
Every percentage where women make the greater major is ~$200 less in median salary

# Appendix

# Looking at sample size for each major
Used to determine the sample size filter to set for analysis
```{r}
majors_processed %>% 
      ggplot(aes(Sample_size, Median)) +
      geom_point() + 
      geom_text(aes(label = Major), check_overlap = TRUE, 
                vjust = 1, hjust = 1) + 
      scale_x_log10() + 
      labs(x = "Sample Size of Respondents", 
           y = "Median Salary") + 
      scale_y_continuous(labels = dollar_format())
```



```{r}
knitr::knit_exit()
```

Scrape work

# Top 20 Majors by Total Graduates
```{r}
majors_processed %>% 
   mutate(Major = fct_reorder(Major, Total)) %>% 
   arrange(desc(Total)) %>% 
   head(20) %>% 
   ggplot(aes(Major, Total, fill = Major_category)) +
   geom_col() + 
   coord_flip() +
   scale_y_continuous(labels = comma_format()) + 
   labs(x = "",
        y = "Total Graduates", 
        fill = "Major Category:") + 
   theme(legend.position = "bottom")
```

# What is the median salary for each major category
```{r}
majors_processed %>% 
      group_by(Major_category) %>% 
      summarize(Median = median(Median)) %>% 
      mutate(Major_category = fct_reorder(Major_category, Median)) %>% 
      ggplot(aes(x = Major_category, y = Median, fill = Major_category)) + 
      geom_col() + 
      scale_y_continuous(labels = dollar_format()) + 
      coord_flip() + 
      labs(x = "", 
           y = "Median Salary", 
           fill = "Major Category:") + 
      theme(legend.position = "bottom")
```

# Majors with the lowest salaries: 
```{r}
majors_processed %>% 
      filter(Sample_size >= 100) %>% 
      tail(20) %>% 
      ggplot(aes(Major, Median, color = Major_category)) + 
      geom_point() + 
      geom_errorbar(aes(ymin = P25th, ymax = P75th)) + 
      expand_limits(y = 0) + 
      scale_y_continuous(labels = dollar_format()) + 
      coord_flip() + 
      labs(title = "What Are the Lowest-Earning Majors", 
           subtitle = "Bottom 20 Majors With At Least 100 Graduates Surveys. Bars Represent 25th and 75th Percentile",
           y = "Median Salary of Graduates", 
           x = "") + 
      theme(legend.position = "bottom") + 
      scale_color_discrete(name = "Major Category:")
```

# Linear Model for Median salary by Share of Women for each Major Category
```{r}
library(ggrepel)

by_major_category %>% 
   ggplot(aes(ShareWomen, MedianSalary)) + 
   geom_point() + 
   geom_smooth(method = lm) + 
   geom_text_repel(aes(label = Major_category), force = .2) + 
   expand_limits(y = 0) + 
   scale_y_continuous(labels = dollar_format()) + 
   scale_x_continuous(labels = scales::percent) + 
   labs(x = "Share of Women", 
        y = "Median Salary")
```

# What is the Correlation of % of Women and the Average Salary
```{r}
library(broom)

majors_processed %>% 
   select(Major, Major_category, Total, ShareWomen, Sample_size, Median) %>% 
   add_count(Major_category) %>% 
   filter(n >= 10) %>% 
   nest(-Major_category) %>% 
   mutate(model = map(data, ~lm(Median ~ ShareWomen, data = ., weights = Sample_size)), 
          tidied = map(model, tidy)) %>% 
   unnest(tidied) %>% 
   filter(term == "ShareWomen") %>% 
   arrange(estimate) %>% 
   mutate(fdr = p.adjust(p.value, method = "fdr"))
```